Hierarchical Reverberation Mapping

### 2013-12-03 Paper/ms.tex
Acknowledge Stephen
Tweaks

\section{The Single Object Model}\label{sec:single_object}
If the continuum light curve of an AGN
is described by a function $y(t)$, then the line
light curve $l(t)$ is given by
\begin{eqnarray}
l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) + C\right] \, d\tau
\end{eqnarray}
where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
and $A$ and $C$ are response
coefficients. The idea of reverberation mapping is to use noisy measurements
of $y(t)$ and $l(t)$ to infer the transfer function $\Psi(\tau)$ or a summary
of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
Throughout this letter we consider $y(t)$ and $l(t)$ in flux
units, as opposed to magnitudes, and consider $\bar{\tau}$ as
the definition of ``the lag'' of an AGN.

@@

Each object in the sample had its own transfer function parameters. The upper
limit $b$ of the transfer function was simulated using a log-normal distribution
with a median value of 10 days, and the standard deviation of $\ln(b)$ was
0.3. Given $b$, $a$ was simulated from a uniform distribution between $0$ and
$a$. The resulting distribution of lags $\bar{\tau} = (a+b)/2$ is very well
approximated by a lognormal distribution with a median of 7.4 days and width
(quantified by the standard deviation of $\log_{10}(\bar{\tau})$) of 0.157.
The response amplitudes $A$ and $C$ were set to 0.5 and 0 respectively, for
all objects.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/data.eps}
\caption{Three simulated data sets, out of a total of 100. It is difficult to
infer the lag $\bar{\tau}$ for any of these objects (although there is some
information available). See Figure~\ref{fig:example_posteriors} for the
$\bar{\tau}$ posterior distributions for these three data sets.
\label{fig:data}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{Figures/ccf.eps}
\caption{The stacked cross-correlation function of the simulated data.
A clear peak is seen around $\tau \approx 10$ days, but the stacked CCF has a
large width. It is difficult to interpret the cause of this width, and to
determine whether the width is due to uncertainty or diversity in the sample
of AGN. These difficulties motivate the hierarchical Bayesian model.
\label{fig:ccf}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/example_posteriors.eps}
\caption{Samples from the posterior distribution for $\log_{10}(\bar{\tau})$
for three objects, each analysed separately with the single-object model. For
the first object, there is a moderate ``detection'' of a lag at about 10 days
(although there is a small second mode above 100 days, which can be understood
by inspecting the data in Figure~\ref{fig:data}).
The second object's lag was not well constrained,
and the third object's data only provided an upper limit on its lag.
\label{fig:example_posteriors}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution $(\mu = 0.867, \sigma = 0.157)$
is indicated by the white star symbol. $\mu = 0.867$ corresponds to a typical
lag of 7.4 days.\label{fig:posterior}}
\end{center}
\end{figure}

The marginal posterior distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
$\mu = 0.838 \pm 0.047$, and the prediction about $\log_{10}(\bar{\tau})$
may be summarised as $\log_{10}(\bar{\tau}) = 0.838 \pm 0.215$. The Bayesian
approach has clearly separated the uncertainty about $\mu$ from the diversity of the
sample, described by $\sigma$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.35]{Figures/posterior2.eps}
\caption{The marginal posterior distribution for $\mu$, the 
hyperparameter describing the center of the distribution for
$\log_{10}\left(\bar{\tau}\right)$, is plotted as the solid line.
\label{fig:posterior2}}
\end{center}
\end{figure}

@@

\section*{Acknowledgements}
It is a pleasure to thank Tommaso Treu, Anna Pancoast (UCSB), and
Brandon Kelly (UCSB) for many
useful conversations about reverberation mapping. The STAN ({\tt mc-stan.org})
team provided helpful advice about the use of their software. BJB is partially
supported by the Marsden Fund (Royal Society of New Zealand).

>>>>

\vspace{-0.5cm}
\section{The Single Object Model}\label{sec:single_object}
If the continuum light curve of an AGN
is described by a function $y(t)$, then the line
light curve $l(t)$ is given by
\begin{eqnarray}
l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) + C\right] \, d\tau
\end{eqnarray}
where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
and $A$ and $C$ are response
coefficients. The idea of reverberation mapping is to use noisy measurements
of $y(t)$ and $l(t)$ to infer the transfer function $\Psi(\tau)$ or a summary
of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
Throughout this letter we consider $y(t)$ and $l(t)$ in flux
units, as opposed to magnitudes, and consider $\bar{\tau}$ as
the definition of ``the lag'' of an AGN.

@@

Each object in the sample had its own transfer function parameters. The upper
limit $b$ of the transfer function was simulated using a log-normal distribution
with a median value of 10 days, and the standard deviation of $\ln(b)$ was
0.3. Given $b$, $a$ was simulated from a uniform distribution between $0$ and
$a$. The resulting distribution of lags $\bar{\tau} = (a+b)/2$ is very well
approximated by a lognormal distribution with a median of 7.4 days and width
(quantified by the standard deviation of $\log_{10}(\bar{\tau})$) of 0.157
(these two quantities are the ones we will infer using the hierarchical model).
The response amplitudes $A$ and $C$ were set to 0.5 and 0 respectively, for
all objects.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/data.eps}
\caption{Three simulated data sets, out of a total of 100. It is difficult to
infer the lag $\bar{\tau}$ for any of these objects (although there is some
information available). See Figure~\ref{fig:example_posteriors} for the
$\bar{\tau}$ posterior distributions for these three data sets.
\label{fig:data}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.35]{Figures/ccf.eps}
\caption{The stacked cross-correlation function of the simulated data.
A clear peak is seen around $\tau \approx 10$ days, but the stacked CCF has a
large width. It is difficult to interpret the cause of this width, and to
determine whether the width is due to uncertainty or diversity in the sample
of AGN. These difficulties motivate the hierarchical Bayesian model.
\label{fig:ccf}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/example_posteriors.eps}
\caption{Samples from the posterior distribution for $\log_{10}(\bar{\tau})$
for three objects whose data sets are shown in Figure~\ref{fig:data}.
These posteriors were obtained by analysing each object separately with the
single-object model. For
the first object, there is a moderate ``detection'' of a lag at about 10 days
(although there is a small second mode above 100 days, which can be understood
by inspecting the data in Figure~\ref{fig:data}).
The second object's lag was not well constrained,
and the third object's data only provided an upper limit on its lag.
\label{fig:example_posteriors}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution $(\mu = 0.867, \sigma = 0.157)$
is indicated by the white star symbol. $\mu = 0.867$ corresponds to a typical
lag of 7.4 days.\label{fig:posterior}}
\end{center}
\end{figure}

The marginal posterior distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
$\mu = 0.838 \pm 0.047$ (consistent with the known input value of
$0.867 \approx \log_{10}(7.4)$),
and the prediction about $\log_{10}(\bar{\tau})$
may be summarised as $\log_{10}(\bar{\tau}) = 0.838 \pm 0.215$. The Bayesian
approach has clearly separated the uncertainty about $\mu$ from the diversity of the
sample, described by $\sigma$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.3]{Figures/posterior2.eps}
\caption{The marginal posterior distribution for $\mu$, the 
hyperparameter describing the center of the distribution for
$\log_{10}\left(\bar{\tau}\right)$, is plotted as the solid line.
\label{fig:posterior2}}
\end{center}
\end{figure}

@@

\section*{Acknowledgements}
It is a pleasure to thank Tommaso Treu, Anna Pancoast (UCSB), and
Brandon Kelly (UCSB) for many
useful conversations about reverberation mapping. The STAN ({\tt mc-stan.org})
team provided helpful advice about the use of their software. BJB is partially
supported by the Marsden Fund (Royal Society of New Zealand). We are grateful
to the referee, Stephen Fine, for his helpful comments.
